---
title: "GG-Plot"
output: pdf_document
---

```
install.packages("tidyverse")
install.packages("scales")
install.packages("tsibble")
```

```{r load packages, warning = FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(scales))
knitr::opts_chunk$set(fig.width = 5, fig.height = 2, fig.align = "center")
```


Consider the following plot. Don't concern yourself with the code at this point.

```{r, fig.width = 5, fig.height = 2}
gapminder %>% 
  filter(year == 2007) %>% 
  mutate(continent = fct_infreq(continent)) %>% 
  ggplot(aes(continent)) +
  geom_bar() +
  theme_bw()
```

Fill in the seven grammar components for this plot.

| Grammar Component     | Specification |
|-----------------------|---------------|
| __data__              | `gapminder` |
| __aesthetic mapping__ | x = continent, y = count |
| __geometric object__  | bars |
| scale                 | Linear |
| statistical transform | count |
| coordinate system     | rectangular |
| facetting             | no |


```
mauna <- tsibble::as_tsibble(co2) %>% 
   rename(month = index, conc = value)
```
Produce a line chart showing the concentration over time. Specifically, the plot should have the following grammar components:

| Grammar Component     | Specification |
|-----------------------|---------------|
| __data__              | `mauna` |
| __aesthetic mapping__ | x: month, y: conc |
| __geometric object__  | lines |
| scale                 | linear |
| statistical transform | none |
| coordinate system     | rectangular |
| facetting             | none |

Fill in the blanks to obtain the plot:

```{r, fig.width = 5, fig.height = 2}
ggplot(mauna, aes(month, conc)) +
  geom_line()
```

```{r, fig.width = 5, fig.height = 2}
ggplot(mauna) +
  geom_point(aes(x = month, y = conc))
```
